---
title: "HW 2"
author: "Lindsay Beyak"
date: "2/19/2021"
output:
  word_document: default
  html_document: default
---

#### Exercise 1

The USArrests dataset contains arrests that occurred in the USA in 1973 for assault, murder, and rape.Each of the 50 states are listed with 4 columns measured numerically. The 'Murder', 'Arrest', and Rape columns indicate arrests (per 100,000), while the 'UrbanPop' column represents the percentage urban population.

```{r}
library(tidyverse)
USArrests

typeof(USArrests)

length(USArrests)

dim(USArrests)
```
#### Exercise 2

Based on the following code, the state with the most Assaults is North Carolina with 337. 

```{r echo = TRUE, error = FALSE}

map_dbl(USArrests, max)
```

#### Exercise 3
```{r}
library(nycflights13)
flights
``` 

#### Exercise 4
A tibble is a data frame that is more unified than a traditional R data frame. Tibble is part of the tidyverse package. It is a more organized data frame to give a cleaner overview of the columns and rows. 

```{r}
#counts for length of columns and rows
length(flights)
nrow(flights)
ncol(flights)

#Tibble confirmations for flights
count(flights)
is_tibble(flights)
class(flights)
```
#### Exercise 5

Below shows the code to reveal each column type of the flights tibble. 
```{r}
typeflcol <- vector("list", ncol(nycflights13::flights))
names(typeflcol) <- names(nycflights13::flights)
for (i in names(nycflights13::flights)) {
  typeflcol[[i]] <- class(nycflights13::flights[[i]])
}
typeflcol
```

#### Exercise 6

```{r}

imodels <- iris %>%
  split(.$Species) %>%
  map(~lm(Sepal.Width ~ Sepal.Length, data = .))
imodels
```

#### Exercise 7 

```{r}
V <- list(12, 22, 27, 31.5, NA, 39, "east")
V

#7a Length of the list
length(V)

#7b Extract the missing value
V[is.na(V)]

#7c Third object extracted
V[3]

#7d Extracting the character string and the minimum number
V[min(1:6)]
V[7]

#7e 7th line of code is a character object
str(V)

